---
title: "Output Summary from BLasso"
author: "Oscar Gonzalez-Recio"
date: " January 14th, 2021"
output:
  html_document: 
    code_folding: hide
    collapsed: yes
    fig_caption: yes
    fig_width: 6
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
  pdf_document: # options pour sorties pdf
    toc: yes
    toc_depth: '3'
  word_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pander) # allow a better impression of tables

```


```{r, output_files, include='TRUE'}

 beta_hat<-read.table("SOL_SNPs.trait")
 beta<-read.table("Beta.txt")

 pred_train<-read.table("GEBV_GRS.txt",header=T)
 pred_test<-read.table("testing.pred.txt",header = T)
 y_real<-read.table("yTRUE.txt")
```


# PREDICTIVE ACCURACY in the testing set

```{r, include='FALSE'}

	  ytrain<-read.table(file='training_regression.txt',header=F)


```

The Pearson correlation between observed and predicted phenotype in the training set was `r round(cor(pred_train$GEBV,y_real$V1[1:length(pred_train$GEBV)]), 2)`.

Next is the scatter plot of the predicted and observed phenotypes in the training set.

```{r, predictive_accuracy_train, include='TRUE'}


 plot(pred_train$GEBV,y_real$V1[1:length(pred_train$GEBV)],xlab="yHat",ylab="Real y")
 plot(pred_train$GEBV,pred_train$ObservedPhenotype,ylab="yHat",xlab="Observed y")
 lm.fit<-lm(pred_train$ObservedPhenotype~pred_train$GEBV)
 abline(lm.fit,col=2)
```


The variance explained in the model (R2) was `r round( summary(lm.fit)$adj.r.squared , 2)`.

The Pearson correlation between observed and predicted phenotype in the testing set was `r round(cor(pred_test$GEBV_GRS,pred_test$ACTUAL_PHENTP), 2)`.

Next is the scatter plot of the predicted and observed phenotypes in the testing set.

```{r, predictive_accuracy_test, include='TRUE'}


 plot(pred_test$GEBV_GRS,pred_test$ACTUAL_PHENTP,xlab="Prediction",ylab="Observed")
 lm.fit<-lm(pred_test$ACTUAL_PHENTP~pred_test$GEBV_GRS)
 abline(lm.fit,col=2)
```


The variance explained in the model (R2) was `r round( summary(lm.fit)$adj.r.squared , 2)`.

# VARIABLE EFFECT

The features with larger (absolute) effect were:

```{r, variable_importance, include='TRUE'}

beta_hat_subset<-beta_hat[order(abs(beta_hat$V3),decreasing = T),]

pander(beta_hat_subset[1:20,])

```

The distribution of the variable importance was:

```{r, variable_importance2, include='TRUE'}

plot(beta_hat$V3,beta$V1,xlab="beta_Hat",ylab = "beta", main="")

```
